---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries}
# Set up any libraries you need
library(tidyverse)
library(polite)
library(rvest)
library(cancensus)
library(haven)
library(lubridate)
```

# Loading client data

```{r}
cust_dev = read_rds("data-raw/cust_dev.Rds")
customer = read_rds("data-raw/customer.Rds")
cust_sleep = read_rds("data-raw/cust_sleep.Rds")
device = read_rds("data-raw/device.Rds")
```



## Web scraping industry data

```{r}
## add url in here
url <- "https://fitnesstrackerinfohub.netlify.app/."

# Make sure this code is updated appropriately to provide 
# informative user_agent details
target <- bow(url,
              user_agent = "meiyi.wu@utoronto.ca for STA303/1002 project",
              force = TRUE)

# Any details provided in the robots text on crawl delays and 
# which agents are allowed to scrape
target

html <- scrape(target)

device_data <- html %>% 
  html_elements("table") %>% 
  html_table() %>% 
  pluck(1) # added, in case you're getting a list format
```

## Accessing Census data on median household income

```{r}
#install.packages("cancensus")


options(cancensus.api_key = "CensusMapper_f96486bcf9d8f024e333d216e279ea12",
        cancensus.cache_path = "cache") # this sets a folder for your cache


# get all regions at the 2016 Census (2020 not update yet)
regions <- list_census_regions(dataset = "CA16")

regions_filtered <-  regions %>% 
  filter(level == "CSD") %>% # Figure out what CSD means in Census data
  as_census_region_list()

# This can take a while
# We want to get household median income
census_data_csd <- get_census(dataset='CA16', regions = regions_filtered,
                          vectors=c("v_CA16_2397"), 
                          level='CSD', geo_format = "sf")

# Simplify to only needed variables
median_income <- census_data_csd %>% 
  as_tibble() %>% 
  select(CSDuid = GeoUID, contains("median"), Population) %>% 
  mutate(CSDuid = parse_number(CSDuid)) %>%
  rename(hhld_median_inc = 2)
```

# Postal code conversion file
```{r}
#dataset = read_sav("data-raw/pccfNat_fccpNat_082021sav.sav")
postcode = read_rds("data-raw/break_glass_in_case_of_emergency.Rds")
write_rds(postcode,"data/postcode.Rds")
```

# Dataset Merging
```{r}
# Save the dataset 
customer %>% left_join(postcode, by = c("postcode" = "PC")) %>% 
  left_join(median_income, by = "CSDuid") %>% 
  left_join(cust_dev, by = "cust_id") %>% 
  write_rds("data/customer.Rds")
cust_sleep %>% write_rds("data/cust_sleep.Rds")
device_data %>% write_rds("data/device.Rds")
```

# Data Manipulation
```{r}
# Left join customer table with cust_dev with cust_id and left join device by dev_id
customer_info = customer %>% left_join(cust_dev,by="cust_id") %>% left_join(device, by="dev_id")
# Get the postcode income information
postcode_inc = postcode %>% distinct(PC,.keep_all = TRUE) %>% left_join(median_income, by = "CSDuid")
# Get rid of some unnecessary information in the customer_info
customer_info = customer_info %>% left_join(postcode_inc, by = c("postcode" = "PC")) %>% select(-c(postcode, pronouns, dev_id, CSDuid)) 

```

```{r}
# Remove NA only for sex and calculate the original
customer_info = customer_info %>% 
  filter(!is.na(sex)) %>% 
  mutate(age = 
           as.numeric(difftime(Sys.Date(), dob, units = "weeks")) / 52.25) %>%
  select(-dob)


# Age rescale: age = 0 represent min age, age = 1 represent max age
customer_info = customer_info %>% mutate(rescaled_age = 0)
customer_info$age_scale = scales::rescale(customer_info$age)
# Population rescale: population = 0 represent min population, population = 1 represent max population
customer_info = customer_info %>% mutate(rescaled_pop = 0)
customer_info$population_scale = scales::rescale(customer_info$Population)
# hhld_median_inc rescale: hhld_median_inc = 0 represent min hhld_median_inc, hhld_median_inc = 1 represent max hhld_median_inc
customer_info = customer_info %>% mutate(rescaled_med_inc = 0)
customer_info$hhld_median_inc_scale= scales::rescale(customer_info$hhld_median_inc)


# Change emoji to a factor
customer_info = customer_info %>% 
  mutate(skin = case_when(emoji_modifier == "U+1F3FF" ~ "Dark",
                          emoji_modifier == "U+1F3FE" ~ "Medium-dark",
                          emoji_modifier == "U+1F3FD" ~ "Medium",
                          emoji_modifier == "U+1F3FC" ~ "Medium-light",
                          emoji_modifier == "U+1F3FB" ~ "Light", 
                          is.na(emoji_modifier) ~ "Default")) %>% 
  select(-emoji_modifier)

# Convert character to factor
customer_info = customer_info %>%
  mutate(sex = as.factor(sex), 
         device_name = as.factor(device_name),
         line = as.factor(line),
         skin = as.factor(skin))

# Save datasets
write_rds(customer_info, "data/customer.Rds")
write_rds(cust_sleep, "data/cust_sleep.Rds")
```

